### 2019-10-11 paper/methods.tex
adding refueling tables in the Appendix

\section{Model description}
\subsection{Geometry}
The \gls{SD-TMSR} design model was introduced by the \gls{CAS} as a part of  
the strategic project ``Future Advanced Nuclear Energy $-$ Thorium-based 
Molten Salt Reactor System (TMSR)" in 2011 
\cite{li_optimization_2018,jiang2012advanced,li2015analysis,li2017model}. The 
design of \gls{SD-TMSR} is inspired by \gls{MSBR} 
\cite{robertson_conceptual_1971} after some modification in the geometry to 
control the positive temperature coefficient in MSBR. The \gls{SD-TMSR} core 
geometry was described in details by Li \emph{et al.} 
\cite{li_optimization_2018}.
Figure~\ref{fig:ff} illustrates the quarter-core model configuration of the 
\gls{SD-TMSR}. The active zone is a right cylinder with height and diameter 
equal to 460 cm. Assemblies of graphite\footnote{We choose graphite density of 
$2.3$ g/cm$^3$, to validate our results against results in the literature 
\cite{li_optimization_2018,nuttin2005potential}.} hexagonal prisms fill the 
core. The side length of the graphite hexagonal prism was optimized in 
\cite{li_optimization_2018} and found to be 7.5 cm. The liquid fuel circulates 
continuously through the fuel channels that pierces the graphite hexagonal 
prisms. The core is divided into two different zones to enhance 
Th/$^{233}$U breeding performance. The radius of the fuel channels in the 
outer and inner zone are 5 and 3.5 cm, respectively. The axial and radial 
graphite reflectors surround the core to minimize neutron leakage and 
maximize flux in the core. The reflectors are surrounded by B${_4}$C cylinder 
that acts as a radiation shielding. The \gls{SD-TMSR} pressure vessel holds 
the fuel salt, graphite elements, reflector, shielding, intermediate heat 
exchanger (IHX) and made of Ni-based (hastelloy N) alloy. The main 
characteristics of the \gls{SD-TMSR} are listed in Table~\ref{tab:table1}.

@@

\subsection{Fuel composition}
The general composition of the liquid fuel salt in this work is 70LiF - 
17.5BeF$_2$ - 12.5(HM)F$_4$ mole\%, where HM is the heavy metal (mixture of 
thorium and other actinides). The aim of this paper is to simulate the  
operation of \gls{SD-TMSR} for 60 years with different startup fissile 
compositions and without any external feed of fissile $^{233}$U which we 
assumed is unavailable. For that reason, five different types of initial 
fissile materials based on \gls{LEU}, Pu, and \gls{TRU} from LWR SF were 
considered:
\begin{enumerate}[label=(\alph*)]
	\item low-enriched uranium (LEU) (19.79\%);
	\item Pu mixed with \gls{LEU} (19.79\%);
	\item Pu reactor-grade \cite{marka1993explosive};
	\item transuranic (TRU) elements from LWR SF \cite{de2000scenarios};
	\item $^{233}$U for comparison purpose \cite{ashraf2019whole_core}.
\end{enumerate}

@@

For reactor-grade plutonium case, the composition was taken for plutonium 
recovered from the spent fuel composition of commercial \gls{PWR} with the 
average discharge burnup $33$ $GWd/t$ and after $10$ years of cooling before 
reprocessing \cite{oecd1989probabilistic,marka1993explosive}. Similarly, the 
isotopic compositions of \gls{TRU} was taken for the SF of UOX \gls{PWR} 
(after one use, no multi-recycling) with the average discharge $60$ 
$GWd/t$ burnup, and after $5$ years of cooling \cite{de2000scenarios}. 
The molar composition of startup fuel for all five cases is listed in 
Table~\ref{tab:table4}. Meanwhile, the corresponding initial nuclei 
inventories with different types of fuel are summarized in 
Table~\ref{tab:table5}.
\begin{table}  %[!ht]
	\caption{Composition of startup fuel (mole\%)}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{0.16\textwidth} X p{0.17\textwidth} 
	p{0.14\textwidth} X X}
		\hline
		Fuel salt component& \gls{LEU} (19.79\%) & Pu+enriched U (19.79wt\%) 
		& Pu reactor-grade & \gls{TRU}& $^{233}$U \\
		\hline
		LiF&70&70&70&70&70\\
		BeF$_2$&17.5&17.5&17.5&17.5&17.5\\
		ThF$_4$&8.25&7.5&10.75&	8.65&12.3		\\
		UF$_4$&4.25&4.75&&&	0.2		\\
		PuF$_3$&&0.25&1.75&&		\\
		(TRU)F$_3$&&&	&3.85	&\\
		\hline
	\end{tabularx}
	\label{tab:table4}
\end{table}

@@

\section{Methodology and tools}

@@

\section{Feed and extraction rates}
In the present work, two different feed mechanisms are used. The first 
mechanism allows continuous feed flow of thorium from Th stockpile, and 
$^{233}$U from \texttt{pa-decay tank}. In contrast, the second mechanism 
continuously injects Heavy Metal (HM) (excluding Th) and simultaneously feeds  
all or part of produced $^{233}$U from \texttt{Pa-decay tank}. The fission 
products act as poisons in the MSRs; they negatively impacting the reactivity. 
Therefore, \gls{FPs} must be extracted during reactor operation. Consider 
$T_{r}$ as the time during which the total fuel salt is reprocessed and 
$dN_{e}$ as the amount of particular element $e$ with inventory $N_{e}$ that 
the \gls{MSR} extracts during time $dt$; thus \cite{nuttin2005potential}

@@

where $\varepsilon_{e}$ is the removal efficiency. Equation \ref{Equ:1} gives 
the removal constant $\lambda_{e}$ $[s^{-1}]$ (the rate at which the material 
is removed), where $\lambda_{e}=\varepsilon_{e}/T_{r}$. The removal constant 
$\lambda_{e}$ of gaseous and other fission products is precisely calculated 
and summarized in Table~\ref{tab:table6}. The effective reprocessing time for 
the gaseous \gls{FPs} and non-dissolved metals was set to 30 seconds (removal 
constant $\lambda_{e}$ = $-0.0333$ $s^{-1}$), because such elements must be 
extracted promptly and continuously via gas removal system. In contrast, 
extracting the soluble \gls{FPs}, lanthanides, and protactinium can be done by 
the chemical reprocessing (i.e. fluorination and reduction reaction). 
Therefore, the system reprocesses a specific amount of fuel salt daily. In the 
present work, the effective extraction time for soluble \gls{FPs} is 
$\approx$10.59 days ($\lambda_{e}$ = $-1.092\times10^{-6}$ $s^{-1}$), which is 
equivalent to 5 m$^3$/d of chemical reprocessing rate 
\cite{nuttin2005potential,li_optimization_2018}. The effective feed rates of 
the heavy metals (HM) are changed during reactor operation to conserve the 
total fuel mass and criticality.

>>>>

\section{Model description} \label{Model-description}
\subsection{Geometry}
The \gls{SD-TMSR} design model was introduced by the \gls{CAS} as a part of  
the strategic project ``Future Advanced Nuclear Energy $-$ Thorium-based 
Molten Salt Reactor System (TMSR)" in 2011 
\cite{li_optimization_2018,jiang2012advanced,li2015analysis,li2017model}. The 
design of \gls{SD-TMSR} is inspired by \gls{MSBR} 
\cite{robertson_conceptual_1971} after some modification in the geometry to 
control the positive temperature coefficient in MSBR. The \gls{SD-TMSR} core 
geometry was described in details by Li \emph{et al.} 
\cite{li_optimization_2018}.
Figure~\ref{fig:ff} illustrates the quarter-core model configuration of the 
\gls{SD-TMSR}. The active zone is a right cylinder with height and diameter 
equal to 460 cm. Assemblies of graphite\footnote{We choose graphite density of 
$2.3$ g/cm$^3$, to validate our results against results in the literature 
\cite{li_optimization_2018,nuttin2005potential}.} hexagonal prisms fill the 
core. The side length of the graphite hexagonal prism was optimized in 
\cite{li_optimization_2018} and found to be 7.5 cm. The liquid fuel circulates 
continuously through the fuel channels that pierces the graphite hexagonal 
prisms. The core is divided into two different zones to enhance 
Th/$^{233}$U breeding performance. The radius of the fuel channels in the 
outer and inner zone are 5 and 3.5 cm, respectively. The axial and radial 
graphite reflectors surround the core to minimize neutron leakage and 
maximize flux in the core. The reflectors are surrounded by B${_4}$C cylinder 
that acts as a radiation shielding. The \gls{SD-TMSR} pressure vessel holds 
the fuel salt, graphite elements, reflector, shielding, intermediate heat 
exchanger (IHX) and made of Ni-based (hastelloy N) alloy. The main 
characteristics of the \gls{SD-TMSR} are listed in Table~\ref{tab:table1}.

@@

\subsection{Fuel composition}
The general composition of the liquid fuel salt in this work is 70LiF - 
17.5BeF$_2$ - 12.5(HM)F$_4$ mole\%, where HM is the heavy metal (mixture of 
thorium and other actinides). The aim of this paper is to simulate the  
operation of \gls{SD-TMSR} for 60 years with different start-up fissile 
compositions and without any external feed of fissile $^{233}$U which we 
assumed is unavailable. For that reason, five different types of initial 
fissile materials based on \gls{LEU}, Pu, and \gls{TRU} from LWR SF were 
considered:
\begin{enumerate}[label=(\alph*)]
	\item low-enriched uranium (LEU) (19.79\%);
	\item Pu mixed with \gls{LEU} (19.79\%);
	\item Pu reactor-grade \cite{marka1993explosive};
	\item transuranic (TRU) elements from LWR SF \cite{de2000scenarios};
	\item $^{233}$U for comparison purpose \cite{ashraf2019whole_core}.
\end{enumerate}

@@

For reactor-grade plutonium case, the composition was taken for plutonium 
recovered from the spent fuel composition of commercial \gls{PWR} with the 
average discharge burnup $33$ $GWd/t$ and after $10$ years of cooling before 
reprocessing \cite{oecd1989probabilistic,marka1993explosive}. Similarly, the 
isotopic compositions of \gls{TRU} was taken for the SF of UOX \gls{PWR} 
(after one use, no multi-recycling) with the average discharge $60$ 
$GWd/t$ burnup, and after $5$ years of cooling \cite{de2000scenarios}. 
The molar composition of start-up fuel for all five cases is listed in 
Table~\ref{tab:table4}. Meanwhile, the corresponding initial nuclei 
inventories with different types of fuel are summarized in 
Table~\ref{tab:table5}.
\begin{table}  %[!ht]
	\caption{Composition of start-up fuel (mole\%)}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{0.16\textwidth} X p{0.17\textwidth} 
	p{0.14\textwidth} X X}
		\hline
		Fuel salt component& \gls{LEU} (19.79\%) & Pu+enriched U (19.79wt\%) 
		& Pu reactor-grade & \gls{TRU}& $^{233}$U \\
		\hline
		LiF&70&70&70&70&70\\
		BeF$_2$&17.5&17.5&17.5&17.5&17.5\\
		ThF$_4$&8.25&7.5&10.75&	8.65&12.3		\\
		UF$_4$&4.25&4.75&&&	0.2		\\
		PuF$_3$&&0.25&1.75&&		\\
		(TRU)F$_3$&&&	&3.85	&\\
		\hline
	\end{tabularx}
	\label{tab:table4}
\end{table}

@@

\section{Methodology and tools} \label{Methodology-and-tools}

@@

\section{Feed and extraction rates} \label{Feed-and-extraction-rates}
In the present work, two different feed mechanisms are used. The first 
mechanism allows continuous feed flow of thorium from Th stockpile, and 
$^{233}$U from \texttt{pa-decay tank}. In contrast, the second mechanism 
continuously injects Heavy Metal (HM) (excluding Th) and simultaneously feeds  
all or part of produced $^{233}$U from \texttt{Pa-decay tank}. The fission 
products act as poisons in the MSRs; they negatively impacting the reactivity. 
Therefore, \gls{FPs} must be extracted during reactor operation. Consider 
$T_{r}$ as the time during which the total fuel salt is reprocessed and 
$dN_{e}$ as the amount of particular element $e$ with inventory $N_{e}$ that 
the \gls{MSR} extracts during time $dt$; thus \cite{nuttin2005potential}

@@

where $\varepsilon_{e}$ is the removal efficiency. Equation \ref{Equ:1} gives 
the removal constant $\lambda_{e}$ $[s^{-1}]$ (the rate at which the material 
is removed), where $\lambda_{e}=\varepsilon_{e}/T_{r}$. The removal constant 
$\lambda_{e}$ of gaseous and other fission products is precisely calculated 
and summarized in Table~\ref{tab:table6}. The effective reprocessing time for 
the gaseous \gls{FPs} and non-dissolved metals was set to 30 seconds (removal 
constant $\lambda_{e}$ = $-0.0333$ $s^{-1}$), because such elements must be 
extracted promptly and continuously via gas removal system. In contrast, 
extracting the soluble \gls{FPs}, lanthanides, and protactinium can be done by 
the chemical reprocessing (i.e. fluorination and reduction reaction). 
Therefore, the system reprocesses a specific amount of fuel salt daily. In the 
present work, the effective extraction time for soluble \gls{FPs} is 
$\approx$10.59 days ($\lambda_{e}$ = $-1.092\times10^{-6}$ $s^{-1}$), which is 
equivalent to 5 m$^3$/d of chemical reprocessing rate 
\cite{nuttin2005potential,li_optimization_2018}. The effective feed rates of 
the heavy metals (HM) are changed during reactor operation to conserve the 
total fuel mass and criticality. The effective feed rates for Th/$^{233}$U, Pu reactor-grade and TRU cases are listed in Table~\ref{tab:table8}, \ref{tab:table9} and \ref{tab:table10} in Appendix.
